\Large Classifying Vehicles From Automatic Number \\ Plate Recognition Camera Scans

### 2018-01-26 trips.tex
Improved maths, final draft for now. Needs revision/feedback by other authors.

Furthermore, condition ~\ref{e.trip.constraints.1} implies that no two sightings in a trip can be the values of $\tau$ and $\Tau$

How to estimate the values of $\Tau$ and $\tau$ remains

>>>>

Furthermore, if we consider all valid trips of vehicle \emph{k}:

\begin{align}
W^{k} = \left( w^{k}_{(1)}, w^{k}_{(2)}, \ldots, w^{k}_{(N)} \right) \label{e.trip.history}
\end{align}

where \emph{N} is the number of trips of \emph{k}, then there should be no two trips containing the same sighting:

\begin{align}
s^{k}_{(u(i))} \neq s^{k}_{(v(j))}, \forall u,v &= 1, 2, \ldots, N \ , \ u \neq v,  \label{e.trip.history.constraint} \\
\forall i,j &= 1, 2, \ldots, n \ , \ i \neq j \nonumber
\end{align}

where, we consider two sightings of vehicle \emph{k} to be different simply if they were observed at two different points in time:

\begin{equation} \label{e.sighting}
t^{k}_{i} \ne t^{k}_{j} \Rightarrow s^{k}_{i} \ne s^{k}_{j} \ , \ i \ne j
\end{equation}

When identifying trips from GPS traces, . It is easy to see that both $\tau$ and $\Tau$ should be functions of the

but, how to estimate the values of $\Tau$ and $\tau$ remains a. For the rest of this work, we will consider these parameters to be fixed.
